---
title: "My fake manuscript"
output: pdf_document
date: "2024-09-13"
bibliography: references.bib
#csl: ecology-letters.csl
#csl: "https://raw.githubusercontent.com/citation-style-language/styles/master/ecology-letters.csl"
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE, warning = FALSE)
```

## Introduction
This is my fake manuscript using iris dataset. I actually work on fish such as pink salmon (*Oncorhynchus gorbuscha*) but this manuscript is not about salmon. Here I am just demonstrating the cool skills I learned in class :)

I learned how to cite papers in rmd. For example, biodiversity is rapidly changing [@blowes_geography_2019], and glmms are useful for understanding these changes [@bolker_generalized_2009].

Next I am going to show that I can embed code into my rmd file. Check out the following plot


```{r echo = FALSE, results = 'asis'}
library(knitr)
data <- read.csv("../00_rawdata/iris.csv")
```


```{r sepal_width_plot, echo=FALSE, fig.width=8, fig.height=5}
library(ggplot2)

# Create the plot
ggplot(data, aes(x = Species, y = Sepal.Width, fill = Species)) +
  geom_boxplot() +
  labs(title = "",
       x = "Species",
       y = "Sepal width (cm)",
  caption = "") +
  theme_minimal() +
  theme(
    panel.grid.major = element_blank(), 
    panel.grid.minor = element_blank(),  
    axis.line = element_line(color = "black"),
     legend.position = "none",
        plot.caption = element_text(hjust = 0) 
  )
```
**Figure 1.** Boxplot of Sepal Width for Each Iris Species.
```{r, echo = FALSE}
kable(summary(data), align = "lllll", caption = "Summary statistics of the iris dataset")

```


## References