---
title: "My fake manuscript"
output: pdf_document
date: "2024-09-13"
bibliography:
- references.bib
- grateful-refs.bib

#csl: ecology-letters.csl
#csl: "https://raw.githubusercontent.com/citation-style-language/styles/master/ecology-letters.csl"
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE, warning = FALSE)
library(grateful)
library(knitr)
```

## Introduction
This is my fake manuscript using iris dataset. I actually work on fish such as pink salmon (*Oncorhynchus gorbuscha*) but this manuscript is not about salmon. Here I am just demonstrating the cool skills I learned in class :)

I learned how to cite papers in rmd. For example, biodiversity is rapidly changing [@blowes_geography_2019], and glmms are useful for understanding these changes [@bolker_generalized_2009]. 

## Methods
```{r, echo = FALSE}
grateful::cite_packages(output = "paragraph", out.dir = ".")
```


## Results
```{r echo = FALSE, results = 'asis'}
data <- read.csv("../00_rawdata/iris.csv")
```

I found that iris species vary in their sepal width (Figure 1). Pretend that this is another results sentence. And that this is another results sentence with super interesting results.

```{r sepal_width_plot, echo=FALSE, fig.width=4, fig.height=3.5}
library(ggplot2)

# Create the plot
ggplot(data, aes(x = Species, y = Sepal.Width, fill = Species)) +
  geom_boxplot() +
  labs(title = "",
       x = "Species",
       y = "Sepal width (cm)",
  caption = "") +
  theme_minimal() +
  theme(
    panel.grid.major = element_blank(), 
    panel.grid.minor = element_blank(),  
    axis.line = element_line(color = "black"),
     legend.position = "none",
        plot.caption = element_text(hjust = 0) 
  )
```

**Figure 1.** Boxplot of sepal width for each iris species.



Wow look how cool that boxplot looks. It would be great to see a summary stats table. Oh wait, the LDP team taught me how to do that. Let's see if i can figure it out.


**Table 1.** Summary statistics of the iris dataset.
```{r, echo = FALSE}
kable(summary(data), align = "lllll")

```

## Discussion
That's it for my sweet iris paper! Thanks for reading. 


## References